### 2014-06-02 ACL2014/abstract.tex
updated abstract

\begin{abstract}
Many applications from various domains such as World Wide Web, Mobile, and NLP
rely on finding nearest neighbors given a data instance.
Due to the very large scale
(e.g., users' queries from commercial search engines),
computing nearest neighbors is often required to
understand users' intents. However, it is a non-trivial
task as the computational complexity grow significantly with the number of queries.
To challenge the aforementioned problem, we exploit 
\lshf (a.k.a, \lsh) methods and propose 
novel varaints in a distributed computing environment (e.g. Hadoop). 
The experimental results demonstrate our 
proposed variants of \lsh achieve the robust performance with better recall compared with Vanilla \lsh even
when using the same space determined by the number of hash tables .

>>>>

\begin{abstract}
Many applications from various domains such as web search, mobile
browsing, and NLP rely on finding the nearest neighbors of a given
text string from a large database.
Due to the very large scale of data involved 
(e.g., users' queries from commercial search engines),
computing nearest neighbors is the best way to 
%often required to
understand users' intents. 
However, it is a non-trivial
task as the computational complexity grow significantly with the number of queries.
To address this challenge, we exploit 
\lshf (a.k.a, \lsh) methods and propose 
novel varaints in a distributed computing environment (specifically, Hadoop). 
We identify several optimizations which improve performance, suitable
for deployment in very large scale settings. 
The experimental results demonstrate our 
proposed variants of \lsh achieve the robust performance with better
recall compared with ``vanilla'' \lsh,  even
when using the same space determined by the number of hash tables.
